PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-07 qfenv_paper/qf_environment.tex
Moved things to discussion section
SMF evol section

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{4}, 
Ken Wong\altaffilmark{3}, 
Guangtun Zhu\altaffilmark{3}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}

\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).

@@

\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In this section, we calculate the SMF for each of these subsamples.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The width of the SMFs represent the sample variance uncertainties.

As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. Later we compare these trends to SMF results from DEEP2 (\cite{bundy06a}) and zCOSMOS (\cite{Bolzonella:2010aa}). In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$). In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF. In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee. For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end. Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.

@@

We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).

@@

@@

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\cite{Baldry:2006aa}; \cite{Peng:2010aa}). From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching. Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. %However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?

\section{Discussion} \label{sec:discussion}

\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$. From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them. Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass. From our analyses we find the following notable results.

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.

\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\subsection{Evolution of the Stellar Mass Function in Different Environments} \label{sec:smfevol}
In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The width of the SMFs represent the sample variance uncertainties.
%%%%%%% REWRITE AFTER REVISED SMF RESULTS
%As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

%Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. 
In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$). In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF. In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee. For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end. Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.

@@

%We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}

@@

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\cite{Baldry:2006aa}; \cite{Peng:2010aa}). From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching. Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. %However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$. From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them. Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass. From our analyses we find the following notable results.
